koda: Deep Learning-Enhanced Pipeline for Keyword Detection in Document Images

### 2020-01-09 paper/paper.tex
First draft of deep learning paragraph

\documentclass[]{article}

\usepackage{graphicx}
\usepackage[margin=3cm]{geometry}

@@

\begin{figure*}[!htb]
	\includegraphics[width=\linewidth]{canny_gaussian.png}
	\caption{TODO}
	\label{fig:canny_gaussian}
\end{figure*}

@@

\begin{figure*}[htb!]
	\includegraphics[width=\linewidth]{canny_comparison.png}
	\caption{TODO}
	\label{fig:canny_comparison}
\end{figure*}

@@

\begin{figure*}[htb!]
	\includegraphics[width=\linewidth]{label_edge.png}
	\caption{Example of the way a sample is fed to the network.}
	\label{fig:label_edge}
\end{figure*}

@@

\begin{figure*}[htb!]
	\includegraphics[width=\linewidth]{augmented_image.png}
	\caption{Example of Data Augmentation}
	\label{fig:augmented_image}
\end{figure*}

>>>>

\documentclass[a4paper]{article}

\usepackage{graphicx}
\usepackage{float}
\usepackage[margin=3cm]{geometry}

@@

\begin{figure}[!htb]
	\includegraphics[width=\linewidth]{canny_gaussian.png}
	\caption{TODO}
	\label{fig:canny_gaussian}
\end{figure}

@@

\begin{figure}[htb!]
	\includegraphics[width=\linewidth]{canny_comparison.png}
	\caption{TODO}
	\label{fig:canny_comparison}
\end{figure}

@@

\begin{figure}[htb!]
	\includegraphics[width=\linewidth]{label_edge.png}
	\caption{Example of the way a sample is fed to the network.}
	\label{fig:label_edge}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[width=\linewidth]{augmented_image.png}
	\caption{Example of Data Augmentation}
	\label{fig:augmented_image}
\end{figure}

During the training, finding the best compromise between good results and overfitting proved to be a challenging problem. In particular, the \textit{loss function}, in this case \textit{binary crossentropy}, 
was not representative of the model's quality. As it can be seen in Fig. \ref{fig:model_loss}, the loss value of the validation set settles around epoch 40. Despite this, further experimentation shows that the model still improves well beyond that epoch. For this reason, a new approach was needed to evaluate the performances of the model.

\begin{figure}[htb!]
	\centering
	\includegraphics[width=0.7\linewidth]{model_loss.png}
	\caption{Model loss over the first 80 epochs.}
	\label{fig:model_loss}
\end{figure}

Despite being simple, the proposed solution is to save the current model's results over a set of test images after each epoch, as well as saving the model itself. This approach allows a simple comparative analysis, and allowed us to select the best model according to its actual results. Epoch 70 produced the best performing model from a generalization standpoint, while further epochs shown interesting but less effective trends. In particular, as you can see from Fig. \ref{fig:edge_comparison_epoch}, the model at epoch 70 is capable of detecting both (A) and (B) edges fairly well, whereas the one at epoch 140 presented an improved result in (A), removing uninteresting objects from the top portion of the image, but was almost incapable of recognizing edges in (B). This phenomenon could be explained as the model starting to empathize straight lines and discarding curved ones. Unfortunately, the latter are a common case and should be considered, therefore the first model was chosen.

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\linewidth]{edge_comparison_epoch.png}
	\caption{Comparison of the edge detector over different epochs.}
	\label{fig:edge_comparison_epoch}
\end{figure}

An overview of the end result can be seen in Fig. \ref{fig:deep_comparison}, which also shows a comparison with the previous Canny-based approach.

\begin{figure}[htb!]
	\centering
	\makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{deep_edge_comparison.png}}%

	\caption{Comparison of Canny and Deep Learning-based edge detection.}
	\label{fig:deep_comparison}
\end{figure}
